\documentclass{article}[12pt]
\usepackage{graphicx} % Required for inserting images
\usepackage{verbatim} % For writing code
\usepackage{amsmath} % For writing maths
\usepackage{cite} % For citations
\usepackage{hyperref} % For links

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan
    }

\title{Exercise 1: The Academic Report}
\author{Kundhavai M}
\date{03 December 2025}

\begin{document}

\maketitle

\section{Introduction}
In this document, I will be writing on \LaTeX. This will be useful for beginners. I hope the contents are understandable. I have set the timer to one hour. I think I will finish at least 3 sections before the time ends. Please note that whatever I have written is truly based on my knowledge, mistakes might happen.

\section{Syntax}
The basic template and syntax for any document would be: 
\begin{verbatim}
    \documentclass{article}[you may enter the size of font here]
    
    % packages if required, for example
    \usepackage{graphicx} % used mainly for images

    \title{Title of your document}
    \author{Who's writing this?}
    \date{the date}

    \begin{document}
        \maketitle

        \section{Introduction}
            \subsection{The subsection}
                \subsubsection{You can make as many sub section as you want}

    %optional
        \begin{bibliography}
        \end{bibliography}
    \end{document}
\end{verbatim}

I have displayed the code using \textbf{verbatim}. You can also do this by including your code in:

\verb|\begin{verbatim}| \\
\hspace*{3em}\verb|% your code| \\
\hspace*{1.5em}\verb|\end{verbatim}|

\subsection{Bibliography}
For bibliography:
\begin{verbatim}
% use cite for bibliography
\begin{thebibliography}{99} % 99 denotes that the label are upto 99,
                            so please leave identation accordingly.

\bibitem{Label 1}
The reference, Author name, Year

\bibitem{Label 2}
The reference, Author name, Year

\end{thebibliography}
\end{verbatim}

\subsection{Some useful tags}
\verb|\Latex| \longrightarrow \LaTeX \\
\verb|\href{www.google.com}{Google}| \longrightarrow \href{www.google.com}{Google} \\
\verb|\textbf{Sigma}| \longrightarrow \textbf{Sigma} \\
\verb|\hspace*{3em}ABC| \longrightarrow \hspace*{3em}ABC \\

\section{End Statement}
There are 4 more minutes left. I already feel tired now. My brain is totally drained. I could not finish the second page fully. I will try to do the next exercise fully. Let's see. Two more minutes left. What shall I do?? \\
I think that I am just filling the page with random texts. One more minute. I will simply wait for the time to end.
\\
\\
It's exact 09:03 and I am winding it up.

$$THANK \; YOU!!$$

\begin{thebibliography}{99}
\bibitem{The Doc}
\href{https://3.mirrors.in.sahilister.net/ctan/macros/latex/required/graphics/grfguide.pdf}{D.P. Carlisle (2025) \emph{Packages in the 'graphics' bundle} The \LaTeX Project}

\bibitem{overleaf}
\href{https://www.overleaf.com/learn/latex/Bibliography_management_with_bibtex}{\emph{Bibliography management with bibtex} Overleaf Tutorials (2025)}

\bibitem{AI}
My AI buddies
\end{thebibliography}

\end{document}


